Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-25 paper/paper.tex
Modify Experiment section.

\subsection*{Data}
In the following section, we will describe an off-line experiment used to
evaluate our similarity estimators. But first, we provide some details about the
data used for this work. The data, originally from Amazon.com, was acquired from
the Stanford Network Analysis Project\footnote{http://snap.stanford.edu}. It
consists of ~5.6M ratings by ~1.2M users of ~600k music items (e.g. albums and
songs). Each rating is from 1 to 5 stars and is associated with a particular
user and item at a particular time.  For practical reasons, we focus our work on
two subsets of this data. The first consists of item pairs having at least 40
common reviewers (i.e. users that have provided a rating for the item). The
second consists of item pairs having at least 80 common reviewers. As discussed
below, we must confine ourselves to item pairs that have many common reviewers
in order to determine a good approximation of the their true similarity.

\subsection*{Experiment}
Ideally, we would know {\em a priori} the true similarity for a set of item
pairs. But both $TrueSimRand$ and $TrueSimPref$ are theoretical constructs and
not metrics we have access to in the real world.  Fortunately, we can achieve
good approximations of either $TrueSim$ given sufficient data. We therefore
define $GoldSim$ = $Sim_N$ where $N$ is a number large enough that $GoldSim
\approx TrueSim$.

With a measurable $GoldSim$ as our goal, we can implement a simple
predictivity experiment. First, we find pairs of items that have at least 
$N$ common users and calculate their $GoldSim$. Next, for each of these pairs
of items, we withhold user ratings, leaving $n$ common reviewers. This 
simulates a pair of items at a time when there is sparser rating data. 
We repeat this for $n=1,...,N$ to get varying degrees of sparsity. With the
sparse ratings alone, the model in question generates a prediction of the 
$GoldSim$, which is compared to the actual $GoldSim$. This is repeated over 
a large number of test pairs and the average squared error of the prediction 
is calculated for each $n$.

>>>>

\subsection*{Data}
In the following section, we will describe an off-line experiment used to
evaluate our similarity estimators. But first, we provide some details about the
data used for this work. The data, originally from Amazon.com, was acquired from
the Stanford Network Analysis Project\footnote{http://snap.stanford.edu}. It
consists of ~5.6M ratings by ~1.2M users of ~600k music items (e.g. albums and
songs). Each rating is from 1 to 5 stars and is associated with a particular
user and item at a particular time.  For practical reasons, we focus our work on
two subsets of this data. The first consists of the 13,752 item pairs having at
least 40 common users (i.e. users that have provided a rating for the item). The
second consists of the 1,312 item pairs having at least 80 common reviewers. As
discussed below, we must confine ourselves to item pairs that have many common
reviewers in order to determine a good approximation of the their true
similarity.

\subsection*{Experiment}
Ideally, we would know {\em a priori} the true similarity for a set of item
pairs. We could then generate similarity estimates and readily determine the
true error in these estimates. But both $TrueSimRand$ and $TrueSimPref$ are
theoretical constructs and not metrics we have access to in the real world.
Fortunately, we can achieve good approximations of either $TrueSim$ given
sufficient data. We therefore define $GoldSim = Sim_N$ where $N$ is a number
large enough that $GoldSim \approx TrueSim$. With a measurable $GoldSim$ as our
goal, we can implement a simple predictivity experiment.

To obtain good $GoldSim$ values, we work with subsets consisting of item pairs
with at least either $N=40$ and $80$ common users. These choices are a
compromise between having enough data for statistically significant results and
having a sufficiently large $N$ that $GoldSim \approx TrueSim$. Note that even
with $N=80$ the average absolute error in $PearSim$ (i.e. $\left<\left| PearSim
- GoldSim \right|\right>$) is $\approx 0.1$\footnote{See Fig.
  \ref{fig:MSE_SimR}}.

...

First, we find pairs of items that have at least 
$N$ common users and calculate their $GoldSim$. Next, for each of these pairs
of items, we withhold user ratings, leaving $n$ common reviewers. This 
simulates a pair of items at a time when there is sparser rating data. 
We repeat this for $n=1,...,N$ to get varying degrees of sparsity. With the
sparse ratings alone, the model in question generates a prediction of the 
$GoldSim$, which is compared to the actual $GoldSim$. This is repeated over 
a large number of test pairs and the average squared error of the prediction 
is calculated for each $n$.
